\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-14 experience.tex
Updated Fabric model discussion.

\begin{figure}[thb]
\centering
\includegraphics[width=\linewidth]{img/fabricmodel}
\caption{Overview of the key machines (rounded boxes) and interfaces (boxes) in our Fabric model.}
\label{fig:fabric_model}
\end{figure}

@@

>>>>

\begin{figure}[thb]
\centering
\includegraphics[width=\linewidth]{img/fabricmodel}
\caption{Overview of the key machines and interfaces in our Fabric model.}
\label{fig:fabric_model}
\end{figure}

@@

\textbf{Replication example:} In order to replicate a state-mutating operation,
user code at the primary replica 
calls \texttt{IStateReplicator.ReplicateAsync},
passing the serialized operation
object.
The operation is sent to the \texttt{ServiceRuntime},
where it is assigned a \emph{logical sequence number} (LSN);
each operation is assigned a consecutive LSN
to track the total-order in which operations should be applied.
The LSN is sent back to the primary replica
where it is returned from the \texttt{ReplicateAsync} call,
along with a \texttt{Task} object that will ``complete'' once
the operation has been replicated to a majority of
secondaries;
thus, the user code can wait on the \texttt{Task}
before confirming to any clients that the request has been applied reliably.
The \texttt{ServiceRuntime} adds the operation to its list of in-flight
replication requests and sends $n$ events to itself to signal that the request
must be sent to a replica, where $n$ is the number of secondary replicas.
The reason for sending $n$ events to itself instead of simply sending events
directly to each secondary is so that the \texttt{ServiceRuntime}
can process a simulated failure event inbetween the sending of replica requests
to each secondary.
This is an example of where we carefully considered
the granularity of actions so that we could 
model failures appropriately.
The user code at a secondary receives the operation,
applies it and then calls \texttt{Acknowledge} on the operation object;
we implement this to send an event to the \texttt{ReplicaRuntime}
which forwards the acknowledgement to the \texttt{ServiceRuntime}.
Once a majority of secondaries have acknowledged, the
\texttt{ServiceRuntime} removes the replication request from its list
of replication requests
and sends an acknowledgement to the primary,
where the previously returned \texttt{Task} completes.

\subsubsection{Fabric model correctness}
Our model does not attempt to
simulate the internals of Fabric accurately,
as its purpose is to find bugs in the user code
and not in Fabric itself (which we assume to be correct).   
However,
due to lack of documentation,
it is not always clear how Fabric should behave
in certain scenarios.
Thus,
we ran several variants of a simple Fabric service
that logs calls into the user code in order to
reverse-engineer the actual behaviour of Fabric;
we ensured that our model has the same behaviour,
although this is an ongoing process as we encounter
additional scenarios.
A further problem is that our model may contain bugs.
In order to find bugs in our model effectively,
we wrote a \psharp{} service made up of a single machine
which takes the place
of the user code and translation layer in Figure \ref{fig:fabric_model},
for each \texttt{ReplicaRuntime}.
Thus, we were able to run this pure \psharp{} system
under \psharp{}'s systematic testing mode
and uncover many assertion failures within our model.
We tested a scenario where the primary fails at some non-deterministic point
within the execution.

\textbf{Example Fabric model assertion failure:}
In the buggy trace,
the \texttt{ServiceRuntime}
sends an \texttt{EEpochInfo} event to the second
\texttt{ReplicaRuntime}
indicating that this is the first epoch and the
replica will be a secondary.
An \emph{epoch} represents a configuration of primary and
secondary replicas; when a different replica becomes the primary,
this indicates the start of a new epoch.
The \texttt{ReplicaRuntime} acknowledges that it has become
a secondary by responding with the same event type.
The \psharp{} service sends an \texttt{ESecondaryCopyContextOp};
this indicates what state the secondary has
and, thus, what the primary should send to this secondary so that it can catch
up.
The \texttt{ESecondaryCopyContextOp} event is forwarded to the
\texttt{ServiceRuntime}. 
The \texttt{ServiceRuntime} then receives and handles an \texttt{EKillPrimary}
event, which causes the second replica to become the new primary.
Thus,
the \texttt{ServiceRuntime} sends another \texttt{EEpochInfo}
to the second \texttt{ReplicaRuntime}
indicating that this is the second epoch
and the replica will be a primary.
As part of this change,
the \texttt{ReplicaRuntime}
sends an event to the \psharp{} service
indicating that it should stop waiting for
the state to be copied from the old primary to this replica,
which is acknowledged by sending an event to the \texttt{ReplicaRuntime}.
This event causes the \texttt{ReplicaRuntime}
to send an \texttt{ESecondaryCopyStateDone}
event to the \texttt{ServiceRuntime},
which unfortunately responds with an event indicating that the
\texttt{ReplicaRuntime} is now an \emph{active} secondary
(i.e.\ a secondary that has caught up with the primary).
However, this causes an assertion failure because
the \texttt{ReplicaRuntime} is becoming a primary and, thus,
cannot be a secondary.
Our fix to this bug was to ensure that the 
\texttt{ESecondaryCopyStateDone} event was marked as part of the first
epoch (as the \texttt{ReplicaRuntime} had not yet acknowledged the
change to primary); thus, 
the \texttt{ServiceRuntime} ignores the event and does not try to make the
replica an active secondary.

\subsubsection{CScale}
